\Large Classifying Vehicles From Automatic Number \\ Plate Recognition Camera Scans

### 2018-01-25 paper.tex
Added some references

\documentclass[twoside,leqno,twocolumn]{article}
\usepackage{ltexpprt}

@@

\title{\Large Vehicle Classification From Automatic Number \\ Plate Recognition Camera Scans}
\author{Pedro M. Pinto Silva \thanks{School of Computing Science, Newcastle University, United Kingdom}
\and
Matthew Forshaw\footnotemark[1]
\and
Stephen McGough\footnotemark[1]}
\date{}

@@

\bibitem{ReviewTransportation2010}
Chen, B. and Cheng, H.H., 2010. {\em A review of the applications of agent technology in traffic and transportation systems}. IEEE Transactions on Intelligent Transportation Systems, 11(2), pp.485-497.

\bibitem{EvolutionUTMC2013}
Hamilton, A., Waterson, B., Cherrett, T., Robinson, A. and Snell, I., 2013. {\em The evolution of urban traffic control: changing policy and technology}. Transportation planning and technology, 36(1), pp.24-43.

>>>>

\documentclass[twoside,leqno,twocolumn]{article}
\usepackage{ltexpprt}
\usepackage{parskip}

@@

\title{\Large Classifying Vehicles From Automatic Number \\ Plate Recognition Camera Scans}
\author{Pedro M. Pinto Silva \thanks{School of Computing Science, Newcastle University, United Kingdom}
\and
Matthew Forshaw\footnotemark[1]
\and
Stephen McGough\footnotemark[1]}
\date{}

@@

\bibitem{SurveyITS2011}
Zhang, Junping, et al. {\em Data-driven intelligent transportation systems: A survey}. IEEE Transactions on Intelligent Transportation Systems 12.4 (2011): 1624-1639.

\bibitem{EvolutionUTMC2013}
Hamilton, Andrew, et al. {\em The evolution of urban traffic control: changing policy and technology}. Transportation planning and technology 36.1 (2013): 24-43.

\bibitem{Castillo2008}
Castillo, Enrique, José María Menéndez, and Pilar Jiménez. {\em Trip matrix and path flow reconstruction and estimation based on plate scanning and link observations}. Transportation Research Part B: Methodological 42.5 (2008): 455-481.

\bibitem{Hazelton2012}
Parry, Katharina, and Martin L. Hazelton. {\em Estimation of origin-–destination matrices from link counts and sporadic routing data}. Transportation Research Part B: Methodological 46.1 (2012): 175-188.
